---
title       : Census Visualization App
subtitle    : Data Product project
author      : JJconde
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r, echo=FALSE}
library(maps)
library(mapproj)
setwd("C:/Users/Meow/Documents/R/Working Directory/census-app")
source("helpers.R")
counties <- readRDS("data/counties.rds")
counties <- counties[!is.na(counties$white), ]
# Change the significant figures to 3
counties$white <- signif(counties$white, digits=3)
counties$black <- signif(counties$black, digits=3)
counties$hispanic <- signif(counties$hispanic, digits=3)
counties$asian <- signif(counties$asian, digits=3)
# Change the name to upper case
counties$name <- toupper(counties$name)
# Format the name of the columns
names(counties) = c("Name", "Total Population", "White", "Black", "Hispanic", "Asian")
```

## 1 - Data

<b>Have you ever been interested in How the United States look like?</b>


a) The data came from U.S. Census Bureau for 2010.  

b) As good as it gets.  

c) Has a reputation for accuracy.  

---

## 2 - Summary

a) It will show Counties with the highest percentage by Race.  
b) A Five-number summary showing the overall trend.  

```{r, echo=FALSE}
summary(counties$White)
head(counties[order(counties$White, decreasing=TRUE), ], 5)
```

---

## 3 - Map

a) Interactive Heat map of the United States.  
b) You will be able to control the percentage and race.

```{r, echo=FALSE}
percent_map(counties$White, "darkgreen", "% White", 0, 100)
```

---

## 4 - Application

a) Creates a Summary, and a Demographic Map using the 2010 US Census.  

b) You can choose which Demographic to show, and what percent you're looking for.  

c) <b>Summary</b>: This will show the Top 10 Counties for the selected Demographic, and a Five-number summary.

d) <b>Map</b>: Based on the grouping, it will show a Heatmap of the Percentage in each Counties.


